Experiments with Synthetic Data

### 2022-08-12 dev/notebooks/synthetic.qmd

```{julia}
line_charts = Dict()
errorbar_charts = Dict()
for (data_name, res) in results
    line_charts[data_name] = plot(res)
    errorbar_charts[data_name] = plot(res,50)
end
```

>>>>

```{julia}
line_charts = Dict()
errorbar_charts = Dict()
for (data_name, res) in results
    plt = plot(res)
    savefig(plt, joinpath(www_path, "line_chart_$(data_name).png"))
    line_charts[data_name] = plt
    plt = plot(res,maximum(res.output.n))
    savefig(plt, joinpath(www_path, "errorbar_chart_$(data_name).png"))
    errorbar_charts[data_name] = plt
end
```
